Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-09 paper.qmd
Shiny Results

<p>The next tab is the <em>Chosen bird</em> tab. In the <em>Table</em> nested tab: first, we have a page that shows the immediate data for the bird that was chosen from its deployment, then we have a map of the locations where this bird has pinged a receiver.In the <em>Group</em> nested tab we have a similar map, but it shows the pings for each of the birds deployed from the same deployment site. The lines are weighted by the frequency of the amount of birds that travelled there. </p>

@@

### <em>About</em>

>>>>

<p>The next tab is the <em>Chosen bird</em> tab. In the <em>Table</em> nested tab: first, we have a page that shows the immediate data for the bird that was chosen from its deployment, then we have a map of the locations where this bird has pinged a receiver. In the <em>Group</em> nested tab we have a similar map, but it shows the pings for each of the birds deployed from the same deployment site. The lines are weighted by the frequency of the amount of birds that travelled there.</p>

@@

### <em>About</em>
<p>The <em>About</em> includes page includes three tabs: <em>Abstract</em>, <em>Data</em>, and <em>Adirondack Deployments</em>. The <Abstract> tab simply includes the abstract for this project. The <em>Data</em> tab includes a data table for all of the Evening Grosbeak data used for these visualizations. The <em>Adirondack Deployments</em> tab includes a data table specfically for all of the Evening Grosbeak data from birds that were deployed from the Adirondack Region.</p>
